Spin canonical divisors of log stacky curves

### 2015-06-28 stacky_write_up/spin_cring.tex
add coln to g0 sat table, change ref to table

\begin{longtable}
	{| c | c |}
	\caption{Genus 0 Saturation}
	\label{table:g-0-sat}

@@

	\hline
	Signature & Saturation \\
	\hline
	\hline

	$(0; 3, 3, 3; 0)$ & $\infty$ \\	\hline

	$(0; 3, 3, 5; 0)$ & $18$ \\	\hline

	$(0; 3, 3, 7; 0)$ & $12$ \\	\hline

	$(0; 3, 3, 9; 0)$ & $12$ \\	\hline

	$(0; 3, 5, 5; 0)$ & $8$ \\	\hline

	$(0; 5, 5, 5; 0)$ & $8$ \\	\hline

	$(0; 3, 3, 3, 3; 0)$ & $6$ \\	\hline

@@

	$(0; 3, 3, k; 0)$ & $9$ \\	\hline

	$(0; a, b, c; 0)$ & $5$ \\	\hline

	$(0; e_1, \ldots, e_r; 0)$ & $3$ \\	\hline
\end{longtable}

\todo{I see it says this above, but I think in the table, it should be made clear exactly what the hypotheses on $k,a,b,c,e_i$ are.}

@@

\noindent
is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
\geq 0$. Since $\sigma_2$ has saturation $s = 5$, as noted in
Subsection ~\ref{ssec:g_0_saturation}, then this map is surjective
when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).

@@

@@

\begin{rem}
These cases give all of the exceptions to the $e$ and $2e$ bounds on
the generator and relation degree. Notice that each of these
exceptional cases, apart from $(0; 3, 5, 7; 0)$, corresponds to a
signature with saturation not equal to
3, 5, or 9. as seen in the table in Subsection
~\ref{ssec:g_0_saturation}. Heuristically, these exceptional saturations can be viewed as
``forcing'' generators (and thus relations) to lie in higher degrees than
expected.
\end{rem}

@@

If $r > 5$, then we can use Lemma
~\ref{lem:sat-3} to add stacky points with
stabilizer order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat-3} (recall from Subsection ~\ref
{ssec:g_0_saturation} that $\sat(\Eff(\sigma_{11})) = 3$), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat-3} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, these cases satisfy all of the
conditions of Lemma ~\ref{lem:raise-stacky-order}.

>>>>

\begin{longtable}
	{| c | c || c |}
	\caption{Genus 0 Saturation}
	\label{table:g-0-sat}

@@

	\hline
	Signature & Note & Saturation \\
	\hline
	\hline

	$(0; 3, 3, 3; 0)$ & & $\infty$ \\	\hline

	$(0; 3, 3, 5; 0)$ & & $18$ \\	\hline

	$(0; 3, 3, 7; 0)$ & & $12$ \\	\hline

	$(0; 3, 3, 9; 0)$ & & $12$ \\	\hline

	$(0; 3, 5, 5; 0)$ & & $8$ \\	\hline

	$(0; 5, 5, 5; 0)$ & & $8$ \\	\hline

	$(0; 3, 3, 3, 3; 0)$ & & $6$ \\	\hline

@@

	$(0; 3, 3, k; 0)$ & $k > 9$ & $9$ \\	\hline

	$(0; a, b, c; 0)$ & not listed above & $5$ \\	\hline

	$(0; e_1, \ldots, e_r; 0)$ & not listed above & $3$ \\	\hline
\end{longtable}

@@

\noindent
is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
\geq 0$. Since $\sigma_2$ has saturation $s = 5$, as noted in
Table ~\ref{table:g-0-sat}, then this map is surjective
when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).

@@

\todo{induct on cases?}

@@

\begin{rem}
These cases give all of the exceptions to the $e$ and $2e$ bounds on
the generator and relation degree. Notice that each of these
exceptional cases, apart from $(0; 3, 5, 7; 0)$, corresponds to a
signature with saturation not equal to
3, 5, or 9. as seen in Table ~\ref{table:g-0-sat}. Heuristically,
these exceptional saturations can be viewed as ``forcing'' generators
(and thus relations) to lie in higher degrees than expected.
\end{rem}

@@

If $r > 5$, then we can use Lemma
~\ref{lem:sat-3} to add stacky points with
stabilizer order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat-3} (recall from Table ~\ref
{table:g-0-sat} that $\sat(\Eff(\sigma_{11})) = 3$), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat-3} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, these cases satisfy all of the
conditions of Lemma ~\ref{lem:raise-stacky-order}.
